Composing Secure Compilers

### 2021-10-19 prisc.tex
Add references

Compilers translate programs from a source to a target programming language.
Secure Compilation studies the preservation of security properties and hyperproperties when compiling a source to a target program.
Robust Compilation~\cite{abate2019} is a novel compiler property that does not require the compiler to add such unnecessary measures.
Informally, if a given (partial) source program linked with an arbitrary source context satisfies some properties of interest, so should its compiled version linked with an arbitrary target context.
Even though there exist robust compilers, they are far from practical.
Real-world compilers consist of several smaller compilers that are composed with each other in a certain way.
A prominent example would be any compiler based on the LLVM toolchain~\cite{lattner04}, whose optimization pipeline consists of many passes, which one can view as independent compilers composed to achieve speedups.
To the best of our knowledge, current work does not discuss which properties are preserved by compilation chains.

>>>>

Compilers translate programs from a source to a target programming language.
Secure Compilation studies the preservation of security properties and hyperproperties when compiling a source to a target program.
Robust Compilation~\cite{patrignani18,abate2019,patrignani19,patrignani21} is a novel compiler property that does not require the compiler to add such unnecessary measures.
Informally, if a given (partial) source program linked with an arbitrary source context satisfies some properties of interest, so should its compiled version linked with an arbitrary target context.
Even though there exist robust compilers, they are far from practical.
Real-world compilers consist of several smaller compilers that are composed with each other in a certain way.
A prominent example would be any compiler based on the LLVM toolchain~\cite{lattner04}, whose optimization pipeline consists of many passes, which one can view as independent compilers composed to achieve speedups.
To the best of our knowledge, current work does not discuss which properties are preserved by compilation chains.
